### 2022-05-19 supplement.Rmd
Proof reading by A.E., A.-S.K.

# Summarise the estimated correlations
(summ_ri_empirical <- print_num(summary(ri_empirical)))
```

@@

5. Compute the observed correlation between conditions based on a rearranged equation by @cohen1988: $$r=\frac{{SD}_\text{diff}^2-{SD}_\text{novel}^2-{SD}_\text{familiar}}{-2\cdot{SD}_\text{novel}^2\cdot{SD}_\text{familiar}^2}$$

Across these $`r nrow(dat_ri_empirical)`$ experiments, the average observed correlation was $r = `r summ_ri_empirical["Mean"]`$ (median $r = `r summ_ri_empirical["Median"]`$, range [`r summ_ri_empirical["Min."]`, `r summ_ri_empirical["Max."]`]). However, we decided to assume a correlation of $r  = 0.50$ when computing the effect size ${SE}_\text{rotation}$ for all `r descriptives$n_experiments` experiments. This was to ensure the comparability of our methods to meta-analyses of between-participant studies [@cohen1988; @lakens2013; @morris2002]. To  evaluate the robustness of our Bayesian meta-analytic models against the assumption of a correlation of $r  = 0.50$, we ran a sensitivity analysis (Supplementary Tables\ \@ref(tab:tabs7) and \@ref(tab:tabs8)).

@@

We used trim-and-fill analysis and selection models to examine if and how our meta-analytic results would change under different degrees of publication bias. For both of these types of models, we used a simplified two-level version of our frequentist three-level model as a basis. In our first step, we computed a trim-and-fill model [@duval2000] by imputing possible effect sizes of non-published experiments. This new model produces a symmetric funnel plot with no association between effect sizes and standard errors (Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11); Supplementary Fig.\ \@ref(fig:figs5)).

@@

  # Re-fit the meta-analysis, leaving out one experiment at a time
  # Using parallelization with `furrr`
  n_cores <- availableCores()
  n_workers <- n_cores %/% n_chains
  plan(multisession, workers = n_workers)
  future_map_dfr(seq_len(nrow(dat_meta)), function(jackknife_index) {
    dat_jackknife <- dat_meta[-jackknife_index, ]
    res_jackknife <- update(
      res_meta,
      newdata = dat_jackknife,
      seed = seed,
      refresh = 0
    )
    print_res_table(
      res_jackknife,
      label_1 = dat_meta$article[jackknife_index],
      label_2 = dat_meta$group[jackknife_index],
      label_col_1 = "Article", label_col_2 = "Experiment"
    )
  }) %>%
    # Show article labels only for the first experiment (row) per article
    mutate(
      Article = if_else(Article == lag(Article, default = ""), "", Article),
    ) -> tabs3

@@

+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ Available statistics                                       | Conversion to standardized mean difference (Hedges' $g$)                                    |
+================================================================+=============================================================================================+
| \ \ (1\) Cohen's $d$ and sample size                           | ${df}=2(n-1)$;\quad                                                                         |
| [@goulet-pelletier2018; @hedges1985]                           | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$; |
|                                                                | \quad $g_\text{rotation}=d\cdot{J}({df})$                                                   |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (2\) $t$ statistic and sample size [@rosenthal1991]        | $d=\frac{t}{\sqrt{n}}$;\quad then (1)                                                       |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (3\) $F$ statistic and sample size [@lakens2013]           | $t=\sqrt{F}$;\quad then (2\)                                                                |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (4\) Mean difference between conditions [@lakens2013]      | $d=\frac{m_\text{diff}}{{SD}_\text{diff}}$;\quad then (1)                                   |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (5\) Mean looking time and ${SD}$ per condition            | ${SD}_\text{av}=\sqrt{\frac{{SD}_\text{novel}^2+{SD}_\text{familiar}^2}{2}}$;\quad          |
| [@cumming2012]                                                 | $d=\frac{m_\text{novel}-m_\text{familiar}}{{SD}_\text{av}}$;\quad then (1)                  |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (6\) Mean novelty preference score [@lakens2013]           | $d=\frac{m_\text{pref}}{{SD}_\text{pref}}$;\quad then (1)                                   |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+

@@

+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ Available statistics               | Conversion to standardized mean difference (Hedges' $g$)                                         |
+========================================+==================================================================================================+
| \ \ (1\) Cohen's $d$ and group sizes   | ${df}=n_\text{female}+n_\text{male}-1$; \quad                                                    |
| [@goulet-pelletier2018; @hedges1985]   | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$;\quad |
|                                        | $g_\text{gender}=d\cdot{J({df})}$                                                                |
+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ (2\) $t$ statistic and group sizes | $d=t\sqrt{\frac{1}{n_\text{female}}+\frac{1}{n_\text{male}}}$;\quad then (1)                     |
| [@lakens2013]                          |                                                                                                  |
+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ (3\) $F$ statistic and group sizes | $t=\sqrt{F}$;\quad then (2\)                                                                     |
| [@lakens2013]                          |                                                                                                  |
+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ (4\) Mean differences between\     | ${SD}_\text{pooled}=\sqrt{\frac{(n_\text{female}-1){SD}_\text{female}^2                          |
| \ \ conditions or preference scores    | +(n_\text{male}-1){SD}_\text{male}^2}{df}}$;\quad                                                |
| [@lakens2013]                          | $d=\frac{m_\text{female}-m_\text{male}}{{SD}_\text{pooled}}$;\quad then (1)                      |
+----------------------------------------+--------------------------------------------------------------------------------------------------+

@@

  # Combine two-level, trim-and-fill, and selection models
  tibble(
    res = c(
      list(
        res_freq_2_lvl[[name]],
        res_trim_fill[[name]],
        res_selection_weights[[name]]
      ),
      res_selection_steps[[name]]
    ),
    label_1 = c(
      "Two-level model", "Trim-and-fill model",
      "Selection models", "", "", "", ""
    ),
    label_2 = c(
      "--", "--", "Weight function [0.01, 0.05, 0.30]",
      "One-tailed, moderate bias", "One-tailed, severe bias",
      "Two-tailed, moderate bias", "Two-tailed, severe bias"
    )
  ) %>%
    # Combine and format as a table
    pmap_dfr(
      ~ print_res_freq_table(
        res_freq = ..1, label_1 = ..2, label_2 = ..3,
        label_col_1 = "Model", label_col_2 = "Sub-model",
        print_sigma2s = FALSE
      )
    ) %>%
    select(-Parameter) %>%
    rename(`Hedges' $g$` = Estimate)
}) %>%
  set_names(names(res_freq_2_lvl)) -> tabs_correction

@@

(ref:figs1-caption) **Meta-analysis of gender differences.** A Bayesian three-level meta-analysis provided evidence for a small gender difference in mental rotation performance between male and female infants. White squares indicate the effect sizes (Hedges' $g$) of gender differences in all individual experiments and black lines indicate their 95% confidence intervals. For experiments resulting in a non-significant gender difference and for which the authors did not specify the exact size of this effect, we assumed an effect size of $g = 0.00$. Gray bars depict the 95% and 50% Bayesian credible interval (CrI) based on a Bayesian three-level random-effects model. The last line shows the meta-analytic effect size (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).

@@

```{r, figs3, include=TRUE, fig.height=6, fig.width=12, fig.cap="(ref:figs3-caption)"}
# Extract convergence statistics (Rhat, Neff) from Bayesian results
conv_stats <- with(summary(res_meta), tibble(
  parameter = c(
    "b_Intercept", "sd_article__Intercept", "sd_article:experiment__Intercept"
  ),
  name_expr = c(
    "\"Hedges'\" ~ italic(g)",
    "italic(sigma)[article]",
    "italic(sigma)[experiment]"
  ),
  r_hat = print_num(c(fixed$Rhat, map_dbl(random, ~ .$Rhat)), digits = 4),
  bulk_ess = round(c(fixed$Bulk_ESS, map_dbl(random, ~ .$Bulk_ESS))),
  tail_ess = round(c(fixed$Tail_ESS, map_dbl(random, ~ .$Tail_ESS))),
  r_hat_expr = str_c("italic(widehat(R)) == ", r_hat),
  bulk_ess_expr = str_c("italic(N)[eff(bulk)] == ", bulk_ess),
  tail_ess_expr = str_c("italic(N)[eff(tail)] == ", tail_ess),
  y_pos = c(0.7, 0.75, 0.8)
))

@@

(ref:figs3-caption) **Convergence checks for the Bayesian meta-analysis.** For each of the three parameters in the three-level meta-analytic model, gray traces show the exploration of the posterior distribution by four independent Markov Chain Monte Carlo (MCMC) chains. Overlap of the gray traces as well as random upward and downward fluctuations (rather than systematic drifts) indicate efficient exploration of the posterior distribution. $\widehat{R}$ = potential scale reduction factor, with values close to 1.0 indicating convergence of the chains, $N_\text{eff(bulk)}$ = bulk effective sample size, with larger values indicating better sampling efficiency in the bulk of the distribution (e.g., for estimating the posterior mean), $N_\text{eff(tail)}$ = tail effective sample size, with larger values indicating better sampling efficiency in the tails of the distribution (e.g., for estimating the 95% credible interval [CrI]). Details about these convergence criteria can be found in @vehtari2021.

>>>>

# Summarise the estimated correlations
(summ_ri_empirical <- list(
  mean = mean(ri_empirical, na.rm = TRUE),
  median = median(ri_empirical, na.rm = TRUE),
  min = min(ri_empirical, na.rm = TRUE),
  max = max(ri_empirical, na.rm = TRUE)
) %>%
  map(print_num))
```

@@

5. Compute the observed correlation between conditions based on a rearranged equation by @cohen1988: $$r=\frac{{SD}_\text{diff}^2-{SD}_\text{novel}^2-{SD}_\text{familiar}^2}{-2\cdot{SD}_\text{novel}\cdot{SD}_\text{familiar}}$$

Across these $`r nrow(dat_ri_empirical)`$ experiments, the average observed correlation was $r = `r summ_ri_empirical$mean`$ (median $r = `r summ_ri_empirical$median`$, range [`r summ_ri_empirical$min`, `r summ_ri_empirical$max`]). However, we decided to assume a correlation of $r  = 0.50$ when computing the effect size ${SE}_\text{rotation}$ for all `r descriptives$n_experiments` experiments. This was to ensure the comparability of our methods to meta-analyses of between-participant studies [@cohen1988; @lakens2013; @morris2002]. To  evaluate the robustness of our Bayesian meta-analytic models against the assumption of a correlation of $r  = 0.50$, we ran a sensitivity analysis (Supplementary Tables\ \@ref(tab:tabs7) and \@ref(tab:tabs8)).

@@

We used trim-and-fill analysis and selection models to examine if and how our meta-analytic results would change under different degrees of publication bias. For both of these types of models, we used a simplified two-level version of our frequentist three-level model as a basis. In our first step, we computed a trim-and-fill model by imputing possible effect sizes of non-published experiments [@duval2000]. This new model produces a symmetric funnel plot with no association between effect sizes and standard errors (Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11); Supplementary Fig.\ \@ref(fig:figs5)).

@@

  # Re-fit the meta-analysis, leaving out one experiment at a time
  # Using parallelization with `furrr`
  n_cores <- availableCores()
  n_workers <- n_cores %/% n_chains
  plan(multisession, workers = n_workers)
  future_map_dfr(seq_len(nrow(dat_meta)), function(jackknife_index) {
    dat_jackknife <- dat_meta[-jackknife_index, ]
    res_jackknife <- update(
      res_meta,
      newdata = dat_jackknife,
      seed = seed,
      refresh = 0
    )
    print_res_table(
      res_jackknife,
      label_1 = dat_meta$article[jackknife_index],
      label_2 = dat_meta$group[jackknife_index],
      label_col_1 = "Article", label_col_2 = "Left-out experiment"
    )
  }) %>%
    # Show article labels only for the first experiment (row) per article
    mutate(
      Article = if_else(Article == lag(Article, default = ""), "", Article),
    ) -> tabs3

@@

+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ Available statistics                                       | Conversion to standardized mean difference (Hedges' $g$)                                    |
+================================================================+=============================================================================================+
| \ \ (1\) Cohen's $d$ and sample size                           | ${df}=2(n-1)$;\quad                                                                         |
| [@goulet-pelletier2018; @hedges1985]                           | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$; |
|                                                                | \quad $g_\text{rotation}=d\cdot{J}({df})$                                                   |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (2\) $t$ statistic and sample size [@rosenthal1991]        | $d=\frac{t}{\sqrt{n}}$;\quad then (1)                                                       |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (3\) $F$ statistic and sample size [@lakens2013]           | $t=\sqrt{F}$;\quad then (2\)                                                                |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (4\) Mean difference between conditions [@lakens2013]      | $d=\frac{m_\text{diff}}{{SD}_\text{diff}}$;\quad then (1)                                   |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (5\) Mean looking times$ per condition [@cumming2012]      | ${SD}_\text{av}=\sqrt{\frac{{SD}_\text{novel}^2+{SD}_\text{familiar}^2}{2}}$;\quad          |
|                                                                | $d=\frac{m_\text{novel}-m_\text{familiar}}{{SD}_\text{av}}$;\quad then (1)                  |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (6\) Mean novelty preference score [@lakens2013]           | $d=\frac{m_\text{pref}}{{SD}_\text{pref}}$;\quad then (1)                                   |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+

@@

+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ Available statistics               | Conversion to standardized mean difference (Hedges' $g$)                                         |
+========================================+==================================================================================================+
| \ \ (1\) Cohen's $d$ and group sizes   | ${df}=n_\text{female}+n_\text{male}-2$; \quad                                                    |
| [@goulet-pelletier2018; @hedges1985]   | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$;\quad |
|                                        | $g_\text{gender}=d\cdot{J({df})}$                                                                |
+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ (2\) $t$ statistic and group sizes | $d=t\sqrt{\frac{1}{n_\text{female}}+\frac{1}{n_\text{male}}}$;\quad then (1)                     |
| [@lakens2013]                          |                                                                                                  |
+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ (3\) $F$ statistic and group sizes | $t=\sqrt{F}$;\quad then (2\)                                                                     |
| [@lakens2013]                          |                                                                                                  |
+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ (4\) Mean differences between\     | ${SD}_\text{pooled}=\sqrt{\frac{(n_\text{female}-1){SD}_\text{female}^2                          |
| \ \ conditions or preference scores    | +(n_\text{male}-1){SD}_\text{male}^2}{df}}$;\quad                                                |
| [@lakens2013]                          | $d=\frac{m_\text{female}-m_\text{male}}{{SD}_\text{pooled}}$;\quad then (1)                      |
+----------------------------------------+--------------------------------------------------------------------------------------------------+

@@

  # Combine two-level, trim-and-fill, and selection models
  tibble(
    res = c(
      list(
        res_freq_2_lvl[[name]],
        res_trim_fill[[name]],
        res_selection_weights[[name]]
      ),
      res_selection_steps[[name]]
    ),
    label_1 = c(
      "Two-level model", "Trim-and-fill model",
      "Selection models", "", "", "", ""
    ),
    label_2 = c(
      "--", "--", "Weight function, $P$ cutoffs [0.01, 0.05, 0.30]",
      "One-tailed, moderate bias", "One-tailed, severe bias",
      "Two-tailed, moderate bias", "Two-tailed, severe bias"
    )
  ) %>%
    # Combine and format as a table
    pmap_dfr(
      ~ print_res_freq_table(
        res_freq = ..1, label_1 = ..2, label_2 = ..3,
        label_col_1 = "Model", label_col_2 = "Sub-model",
        print_sigma2s = FALSE
      )
    ) %>%
    select(-Parameter) %>%
    rename(`Hedges' $g$` = Estimate)
}) %>%
  set_names(names(res_freq_2_lvl)) -> tabs_correction

@@

(ref:figs1-caption) **Meta-analysis of gender differences.** A Bayesian three-level meta-analysis provided evidence for a small gender difference in mental rotation performance between male and female infants. White squares indicate the effect sizes (Hedges' $g$) of gender differences in all individual experiments and black lines indicate their 95% confidence intervals. For experiments resulting in a non-significant gender difference and for which the authors did not specify the exact size of this effect, we assumed an effect size of $g = 0.00$. Gray bars depict the 50% and 95% Bayesian credible interval (CrI) based on a Bayesian three-level random-effects model. The last line shows the meta-analytic effect size (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).

@@

```{r, figs3, include=TRUE, fig.height=6, fig.width=12, fig.cap="(ref:figs3-caption)"}
# Extract convergence statistics (Rhat, Neff) from Bayesian results
conv_stats <- with(summary(res_meta), tibble(
  parameter = c(
    "b_Intercept", "sd_article__Intercept", "sd_article:experiment__Intercept"
  ),
  name_expr = c(
    "\"Hedges'\" ~ italic(g)",
    "italic(sigma)[article]",
    "italic(sigma)[experiment]"
  ),
  r_hat = print_num(c(fixed$Rhat, map_dbl(random, ~ .$Rhat)), digits = 4),
  bulk_ess = print_big(c(fixed$Bulk_ESS, map_dbl(random, ~ .$Bulk_ESS))),
  tail_ess = print_big(c(fixed$Tail_ESS, map_dbl(random, ~ .$Tail_ESS))),
  r_hat_expr = str_c("italic(widehat(R)) ~ == ~ \"", r_hat, "\""),
  bulk_ess_expr = str_c("italic(N)[eff(bulk)] ~ == ~ \"", bulk_ess, "\""),
  tail_ess_expr = str_c("italic(N)[eff(tail)] ~ == ~ \"", tail_ess, "\""),
  y_pos = c(0.7, 0.75, 0.8)
))

@@

(ref:figs3-caption) **Convergence checks for the Bayesian meta-analysis.** For each of the three parameters in the three-level meta-analytic model, gray traces show the exploration of the posterior distribution by four independent Markov Chain Monte Carlo (MCMC) chains. Overlap of the gray traces as well as random upward and downward fluctuations (rather than systematic drifts) indicate efficient exploration of the posterior distribution. $\widehat{R}$ = potential scale reduction factor, with values close to 1.00 indicating convergence of the chains, $N_\text{eff(bulk)}$ = bulk effective sample size, with larger values indicating better sampling efficiency in the bulk of the distribution (e.g., for estimating the posterior mean), $N_\text{eff(tail)}$ = tail effective sample size, with larger values indicating better sampling efficiency in the tails of the distribution (e.g., for estimating the 95% credible interval [CrI]). Details about these convergence criteria can be found in @vehtari2021.
